Evaluation of Pre-Trained Models for Many-to-English Translation

### 2024-08-19 paper/paper.tex
updated, now 16 pages

This study's experiments also resulted in a moderately higher overall SacreBLEU score, however, the dataset used here is also significantly less in size than the full Tatoeba challenge dataset \cite{tiedemann-2020-tatoeba-challenge}.

@@

The dataset consists of mostly short sentences. Whether the result of this study stays consistent for longer sentences or documents is not known and should be further looked into. Moreover, the linguistic depth of the sentences is considered low and does not require deep understanding.

>>>>

While this study's experiments resulted in a moderately higher overall SacreBLEU, the dataset used here is also significantly smaller than the full Tatoeba challenge dataset \cite{tiedemann-2020-tatoeba-challenge} that are used in the OPUS-MT reported BLEU. In contrast, this study employs the same set of parallel sentences for all languages, which should lead to more consistent results. Nevertheless, a direct comparison between these results is not fully pertinent.

@@

The dataset consists of mostly short sentences, with little or none linguistic depth. Whether the result of this study stays consistent for longer sentences or documents is not known and should be further looked into. The Tatoeba dataset \cite{tiedemann-2020-tatoeba-challenge} consisting of short sentences has been reported to be too optimistic when evaluated with other datasets that are more realistic \cite{tiedemann-2020-opus-mt}.
